---
title: "Introduction_to_riksdagenAPI"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_riksdagenAPI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

  This package filters speeches based on the user-provided party and date range, 
  and returns the top ten nouns from the speeches.

## Installing the Package

```{r install,eval = FALSE}
install.packages("riskdagenAPI")
```

## Loading the Package

```{r load, eval = FALSE}
library("riskdagenAPI")
```

## Choosing the Parameters

First, type the following values that you are interested in:`start_date`,`end_date`,`type_speech`,`party`,`member`,`size`.

Every value should follow the rules below:

-`start_date`:A string representing the date in `YYYY-MM-DD` format, or use 
`"skip"` to omit this parameter. 

-`end_date`:yyyy-mm-dd or skip.

-`type_speech`:`Nej`or skip.

-`party`:`"c"`, `"l"`, `"kd"`, `"mp"`, `"m"`, `"s"`, `"sd"`, `"v"`, `"-"`, 
`"nyd"` or skip.

-`member`:"ID of member" or skip.

-`size`:`"10"`,`"50"`,`"200"`,`“1000"`,`"2000"`,`"5000"`,`"10000"`.

## Example

Now, use the following function to fetch the data :
```{r example,eval = FALSE}
#Define parameters
start_date <- "2015-01-01"
end_date <- "2024-01-01"
type_speech <- ""          #Use ""to skip this parameter
party <- ""                #Use ""to skip this parameter
member <- "0729710260118"  #ID of member
size <- "1000"             #Size of result
#Fetch the data
result <- get_top_10_nouns(start_date,end_date,type_speech,party,member,size)
print(result)
```



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```